{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-13 documents/charge.tex
testing

@@

On the largest scale, the net charges of the 11 major proteins coded for by the influenza genome

>>>>

Yang et al determine that, to fit their microwave absorption cross-section data, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.

Is such a charge plausible?

On the largest scale, at a pH of 7, the net charges of the 11 proteins coded for by the Influenza A genome only contribute

The polarization potential example that Adair borrows from Frolich, with a membrane potential of 100 V (see []) still only contributes.

$$(4.523 \times 10^-14 \text{m}^2 \cdot 0.01 \text{F/m}^2 \cdot 100 \text{V}) \approx 10^5 e^- $$

@@
